---
title: "BIOS100-Project"
author: "Your Name"
date: "Fall 2025"
output:
  pdf_document:
    df_print: tibble
  html_document:
    df_print: tibble
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
if (!require("tidyverse")) install.packages("tidyverse"); library("tidyverse") #install and load tidyverse
if (!require("neonUtilities")) install.packages("neonUtilities"); library("neonUtilities") #used to download NEON data
```

# Choose NEON Data


Use [Explore Data by Location](https://www.neonscience.org/data#0) to start with a map-based view of of sites.

Or use [Explore Data Products](https://data.neonscience.org/data-products/explore) to start with the kind of data that is available. On the left-hand side Filter, I recommend you stick with the Theme "Organisms, Populations, and Communities", because you've learned the tools to work with that kind of data.

We already explored the mosquito pathogen status for all NEON sites across time, so you choose a different set of data.

Below, type a few sentences on what data you plan on using. Include information on which sites and information which data sets. It may also be appropriate to include information on which year(s) you are examining.

## 1) WHAT DATA DO YOU PLAN ON USING?




# Explore the data to understand it

Load your data. 

## 2) COMPLETE THE CODE CHUNK BELOW

In the code below, fill in details for dpID and site based on what data decided to examine.

```{r}
datalist = loadByProduct(dpID="", site="", check.size = F) 
saveRDS(datalist,file="NEONdatalist_Project")
datalist <- readRDS(file="NEONdatalist_Project")
```

After executing the above code once, add # in front of the first and second line, i.e. the line that starts with datalist = loadByProduct and the line that starts with saveRDS. Commenting out those two lines will run the code much faster each time becuase it will just load the data from the local copy.

Optionally, you may need to load multiple products and store them in different datalist variables.


```{r}
names(datalist)
```

From the list of files downloaded, determine which file as the data you want to look at. Replace the xxx in the code chunk below with the name of the file you will be using. If it is multiple files, include lines of code for each file.

## 3) COMPLETE THE CODE CHUNK BELOW

```{r}
datalist$xxxx
```

Use the select() function to select just those columns from above that appear to contain the interesting data you want to examine. 

If you would like some guidance, go back and reference the steps we did in BIOS100-NEON for the mos_pathogenpooling file. You are repeating those steps here, but for the data in which you are interested.

```{r}
datalist$xxxx |>
  select()
```

Remember that you can examine the description of variables to help understand what field contain the data in which you are interested. You will have replace the 00000 with the number from your file names above, and you will have to fill in the full name of the table inside the quotes. 

```{r}
datalist$variables_00000 |>
  filter(table == "")
```

# Develop a question and a hypotheses

Ask a question that your data has the potential to address. A hypothesis is an informed expectation based on what you know about the system. 

## 4) WHAT IS YOUR QUESTION?



## 5) WHAT IS YOUR HYPOTHESIS




